\section{Discussion}

The result presented above showcased that staggering the grid gave a much better agreement with the theoretical solution, compared to the unstaggered grid scheme. Interestingly one could see that the error of the staggered grid scheme with the coarsest spatial resolution ($\Delta x = 0.05$) is in the same magnitude as the unstaggered grid scheme with the grid resolution of $\Delta x = 0.025$. This result can be used from two points of view. First, this means that when computing a numerical scheme with a unstaggered grid, one can obtain the same error with a staggered grid scheme by using a twice as large grid spacing. This will thus save computational space and time, since the number of grid points will be halved. Another way of viewing this result is that  by using the same grid spacing, staggering the grid will give a much smaller error than using an unstaggered grid. This can thus be used to improve the accuracy of numerical schemes.

One drawback of using a staggered grid scheme is that the scheme requires a smaller Courant number for stability, compared to the unstaggered grid scheme. This means that the time step needs to be smaller, which will increase the computational space and time. However, it was shown that the staggered grid could produce the same error as the unstaggered grid with a twice as large grid spacing, which means that although the scheme uses a smaller time step, it can still save space and time through the use of a larger grid spacing. Thus, although the staggered grid scheme is more limited by the Courant number, it can still be more efficient due to the lowering of the numerical error.


Regarding the Robert-Asselin filter, it showed to lower the error of of both the unstaggered and staggered grid schemes. However the affect of the Robert-Asselin on the unstaggered grid scheme did not lower the error as much as staggering did. However, the Robert-Asselin filter could also be applied to the staggered grid scheme, and showed to lower the error even more, although the effect was of a smaller scale. Thus, the Robert-Asselin filter can be used together with a staggered grid scheme to further lower the error of the numerical scheme. 
